Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-03-27 paper/tidy-missing-data-paper.Rmd
adding some notes from meeting

@@

Other statistical programs represent missingness values as a full-stop, `.`, and allow for recording special missing values as `.a` - `.z`. The special values from these languages break the rule of "keeping one thing in a cell", as they record both the value and the multivariate missingness state. Additionally, special missing values in other statistical programming languages are encoded at a lower level in the fundamental `NA` type, which is not possible in R.

@@

1. **Cohesiveness**: Binding the shadow matrix column-wise to the original data creates a cohesive _nabular_ data format, so that it cannot be out of sync with the data. useful for visualization, summaries, and tracking imputed values. This is discussed in more detail below in \@ref(nabular-data).

@@

```{r clean-data-for-analysis, include = FALSE}

impute_knn <- simputation::impute_knn
dat_house <- housing_cls %>%
  mutate(year = lubridate::year(date),
         # month = lubridate::month(date),
         quarter = lubridate::quarter(date)) %>%
  mutate_at(vars(car, bathroom, bedroom2), as.integer)

>>>>

(principle: clarity of labelling - transparent what the matrix means, because these could equally be "missing" or "present" - for this. Anybody looking at these values)

@@

Other statistical programs (SPSS, SAS, and Stata) represent missingness values as a full-stop, `.`, and allow for recording special missing values as `.a` - `.z`.

SAS, SPSS, and STATA all implement

The special values from these languages break the rule of "keeping one thing in a cell", as they record both the value and the multivariate missingness state. Additionally, special missing values in other statistical programming languages are encoded at a lower level in the fundamental `NA` type, which is not possible in R.

(discuss the principles, rather than what we've done)

(in the same column you have mixed information, which breaks the tidy principle of one column having one type of value)

@@

(change cohesiveness to connectedness)

1. **Connectedness**: Binding the shadow matrix column-wise to the original data creates a single connected _nabular_ data format, so that it cannot be out of sync with the data. useful for visualization, summaries, and tracking imputed values. This is discussed in more detail below in \@ref(nabular-data).

@@

```{r clean-data-for-analysis, include = FALSE}
# add memoise to store the output data for this
impute_knn <- simputation::impute_knn
dat_house <- housing_cls %>%
  mutate(year = lubridate::year(date),
         # month = lubridate::month(date),
         quarter = lubridate::quarter(date)) %>%
  mutate_at(vars(car, bathroom, bedroom2), as.integer)
